\chapter{Acknowledgments}

Firstly, I would like to thank my PhD supervisors for guiding me during this journey.
Rachel, for your continuous help and support.
I have learnt so much from you.
John, for your infinite patience explaining epilepsy concepts to us engineers.
Seb, for your unconditional support and your trust since the first day.
Many thanks also to Beate Diehl for her trust, time and support.

Thanks to my colleagues, who made my time more enjoyable on both sides of the river, and shared wisdom, time, energy and beer with me.
Phil Noonan, Kerstin Kläser, Pedro Borges, Virginia Fernández, Reuben Dorent, Olivier Jaubert, Alejandro Granados, Gloria Romagnoli, Andrés Díaz, Michael Ebner, Nora Mackle, Luis García-Peraza, Oeslle Lucena, Matt Clarkson, Marc Modat, Sam Joutard, Ioana Dobre, Aaron Kujawa, Wenqi Li, Liane Canas, Katie Konyn, Tommy Klinge, David Drobny, and many others. It would have never been the same without you!

Muchísimas gracias también a todos los miembros de mi familia que siempre me han apoyado durante mis estudios, desde la distancia.
Qué suerte tengo de tenerles en mi vida.

I would also like to thank the many anonymous heroes in the open-source software community.
Most of today's research sits on uncountable hours of altruistic work by developers sacrificing part of their free time for the benefit of the community.

I wish to acknowledge \ac{UKRI} for providing the funding for my PhD, and the \ac{i4health} for their support.

Last but definitely not least, I wish to express my eternal gratitude to Sue for bearing with me during these years, for your patience, for your support, for your love.
I feel truly lucky to have you by my side.

\clearpage
\begin{center}
    \thispagestyle{empty}
    \raggedleft
    \vspace*{\fill}
    \textit{A mis hermanos: Javi, Rodri, Jorge y Gonza.}
    \vspace*{\fill}
\end{center}
\clearpage
